STAT 450 Project: Real Estate

### 2020-03-31 src/2nd_draft.Rmd
typo

 - **Prediction power** measures how well models can predict future values. Mean squared prediction power is used to compare the prediction performance across all of our fitted linear predictive models.  MSPE (Mean Squared Predction Error) on test sets is used to measure the prediction power in this study and a smaller MSPE indicates better prediction power.

@@

Also, another advantage of these models is that they help reduce the variance of MSPE, so that MSPE is more stable. For more detials about the two models, please refer to **Reference**.

@@

The p-values in Table 1 have supported that there is nonidentical distributions of mill rates across municipalities and tax classes.

>>>>

 - **Prediction power** measures how well models can predict future values. Mean squared prediction power is used to compare the prediction performance across all of our fitted linear predictive models.  MSPE (Mean Squared Prediction Error) on test sets is used to measure the prediction power in this study and a smaller MSPE indicates better prediction power.

@@

Also, another advantage of these models is that they help reduce the variance of MSPE, so that MSPE is more stable. For more details about the two models, please refer to **Reference**.

@@

The p-values in Table 1 have supported that there are nonidentical distributions of mill rates across municipalities and tax classes.
